Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Update html and edit weibull plot titles

# summ.df %>% 
#   ggplot(., aes(y = dsprsn)) +
#   geom_boxplot()
# 
# summ.df %>% 
#   ggplot(., aes(x = av.disp)) +
#   geom_density(color = "blue") + # for the average dispersal per run
#   geom_density(data = df %>% drop_na(s.id),
#                  aes(x = disp)) + # for every seed
#   theme_bw()
```
### Fit distribution function to seed dispersal data
The end goal here is to understand how variation in animal movement rates can impact seed dispersal patterns. To get a metric of this seed dispersal, we fit a weibull distribution to the seed dispersal data generated by the previous simulation. Every run has 20 seeds, and we did this 100 times, thus we randomly sample 50 seeds to fit a Weibull distribution and get an approximated seed dispersal kernel.

@@

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.scale)) +
  geom_violin() +
  #geom_boxplot(width = 0.1) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="red") +
  theme_bw()

>>>>

# summ.df %>% 
#   ggplot(., aes(y = dsprsn)) +
#   geom_boxplot()
# 
# summ.df %>% 
#   ggplot(., aes(x = av.disp)) +
#   geom_density(color = "blue") + # for the average dispersal per run
#   geom_density(data = df %>% drop_na(s.id),
#                  aes(x = disp)) + # for every seed
#   theme_bw()
```
### Fit distribution function to seed dispersal data

The end goal here is to understand how variation in animal movement rates can impact seed dispersal patterns. To get a metric of this seed dispersal, we fit a weibull distribution to the seed dispersal data generated by the previous simulation. Every run has 20 seeds, and we did this 100 times, thus we randomly sample 50 seeds to fit a Weibull distribution and get an approximated seed dispersal kernel.

@@

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.scale)) +
  geom_violin() +
  #geom_boxplot(width = 0.1) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="red") +
  labs(title = "Scale") +
  theme_bw() -> p1

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.shape)) +
  geom_violin() +
  #geom_boxplot(width = 0.1) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="red") +
  labs(title = "Shape") +
  theme_bw() -> p2

plot_grid(p1, p2)
 ```
